Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

>>>>

Interestingly, the distributions for $s$ and $\tilde s$ do not even need
to be the same. Namely, if $s\sim \rho$ and $\tilde s\sim \tilde \rho$,
then $\partial_\theta V(s) V(\tilde s)$ is not a gradient of either
$(\E_\rho V)^2$ or $(\E_{\tilde \rho}V)^2$. But we can still add $V(\tilde
s)$ to the TD step at $s$ and look for a fixed point. The fixed point of
the above is when, for any $s$, 
\begin{equation}
\E_{a,s',\tilde s|s} \left(r(s,a)-b+\gamma
V(s')-V(s)+(1-\gamma-\alpha)V(\tilde s)\right)=0
\end{equation}
and this does not involve the distribution of $s$, so the unique solution is similar to the above, with expectations under
$\tilde \rho$:
\begin{equation}
V(s)=V^\pi(s)-\E_{\tilde \rho} V^\pi-\frac{b-(1-\gamma)\E_{\tilde
\rho}V^\pi}{\alpha}
\end{equation}
(And if $V_\theta$ is overparameterized, if we converge we converge to
this.) Likewise, the solution for $b$ is as above, and if
$V=V^\pi+\mathrm{cst}$ then 
\begin{equation}
b=(1-\gamma)\E_{\tilde s} V^\pi(\tilde s)=(1-\gamma)\E_{\tilde \rho} V^\pi
\end{equation}

We may even take a single value $s_0$ for $\tilde s$ as a reference point
($\tilde \rho$ a Dirac mass at $s_0$): $V$ would converge to
$V^\pi-V^\pi(s_0)$, and $b$ to $(1-\gamma)V^\pi(s_0)$. This may be the
simplest practical solution. (If changing $s_0$ from time to time, $V$
would have to be shifted by the change of $V^\pi(s_0)$.)
